---
title: "R Notebook"
output: html_notebook
---
---
title: "Correspondence Analysis"
output: html_notebook
---

```{r}
install.packages("ca")
library(ca)
```
# Smoke data

Table containing 5 rows (staff group) and 4 columns (smoking categories), giving the frequencies of smoking categories in each staff group in a fictional organization.

```{r}
data("smoke")
smoke
```

Row I (Staff Groups): SM (Senior managers), JM(Junior Managers), SE(Senior Employees), JE(Junior Employees) and Secretaries 
Columns J (Smoking Habits):  None, Light, Medium and Heavy

```{r}
smoke.ca <- ca(smoke)
smoke.ca

```

The above output has the percentages of explained inertia for all possible dimensions
The second and the third tables above show masses, chi-squared distances of points to their average, inertias and standard coordinates, restricted to 2 dimensions

```{r}
### To see a list of available entries 
names(smoke.ca)
smoke.ca$coord

```
```{r}
summary(smoke.ca)
```
Similar to the above, summary(ca) also presents us with the following information:
* eigenvalues 
* relative percentages of explained inertia of all dimensions
* a scree plot
* cumulated percentages
* principal coordinates for the first 2 dimensions (k=1, k=2)
* Squared correlations (cor) and contributions (ctr) of these points (display next to the coordinate), display in permills
```{r}
## Visualizing using a symmetric map
smoke.ca.plot <- plot(smoke.ca)
smoke.ca.plot
```


```{r}
smoke.ca.biplot <- plot(ca(smoke), mass = TRUE, contrib = "absolute",map = "rowgreen", arrows = c(FALSE, TRUE))
smoke.ca.biplot


```

